Physcraper: A Python package for continually updated gene trees

### 2020-05-22 physcraper_ms.Rmd
outline discussion

Mention statistics provided by PhyloExplorer [@ranwez2009phyloexplorer]

@@

PhyloFinder [@chen2008phylofinder] - a search engine for phylogenetic databases using
trees from TreeBASE - MEH

>>>>

There are many tools that are making use of DNA data repositories in different ways.
Most of them focus on efficient ways to mine the data -- getting the most homologs.
Some focus on accurate ways of mining the data - getting real and clean homologs.
Others focus on refinement of the alignment.
Most focus on generating full trees *de novo*, mainly for regions of the Tree of
Life that have no phylogenetic assessment yet in published studies, but also for
regions that have been already studied and that have phylogenetic data already.

All these tools are great efforts for advancing towards reproducibility in phylogenetics,
a field that has been largely recognised as somewhat artisanal.
We propose adding focus to other sources of information available from data repositories.
DNA data bases have been the focus for long time, but phylogenetic knowledge is
also accumulating fast in open repositories.
Certainly, parts of other tools that might work faster in some ways could be incorporated into the physcraper pipeline.

We emphasize that physcraper takes advantage of the knowledge and intuition of the expert
community to build upon this phylogenetic knowledge, using not only data accumulated in DNA repositories, but phylogenetic knowledge accumulated in tree repositories.
This might help generate new phylogenetic data. But physcraper does not seek to generate full phylogenies *de novo*

Describe again statistics to compare phylogenies provided by physcraper via OpenTreeOfLife.
Mention statistics provided by other tools: PhyloExplorer [@ranwez2009phyloexplorer].
Compare and discuss.

@@

PhyloFinder [@chen2008phylofinder] - a search engine for phylogenetic databases using
trees from TreeBASE - more related to phylotastic's goal than to updating phylogenies
